The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-07-28 brains-protocol.tex
fix/results: phrasing

\newtext{On the whole}, we observe a clear \newtext{attraction} pattern for each feature, with two different classes corresponding to the psychological relevance of each feature for the substitution process.
\newtext{More awkward words along relevant features (less frequent, learned later, or with made of more letters), both globally and with respect to the sentence they appear in, are substituted more often than more common words.
And across all features, words are brought generally closer to the sentence median than what a random process would do.}

>>>>

\newtext{On the whole}, we observe a clear \newtext{attraction} pattern for each feature, with two different classes corresponding to the psychological relevance of each feature for the substitution process.
\newtext{More awkward words along relevant features (less frequent, learned later, or made of more letters), both globally and with respect to the sentence they appear in, are substituted more often than what would happen if targets were picked randomly in the sentences;
conversely, more common words are substituted less.
Finally, across all features, substituted words are attracted towards a point closer to the sentence median than what a random process, semantically plausible or not, would do.}
